Beam-Helicity and Beam-Charge Asymmetries \\ in the Bethe--Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS0607 (v2.2)} \underline{Drafting Committee: DC90 (\today)}

### 2012-01-17 theory.tex
version 2.2

The four-fold differential cross section for the \red{exclusive} leptoproduction of real photons
from an unpolarised target can be written as \cite{Bel02b}
\begin{center}
\begin{equation}
\frac{\textrm{d}^4\sigma}{\textrm{d}x_{\textrm{B}}\textrm{d}Q^{2}\textrm{d}
|t|\textrm{d}\phi} =
\frac{x_{\textrm{B}}e^{6}}{32(2\pi)^{4} Q^{4}\sqrt{1+\epsilon^{2}}}
|\tau|^{2},
\end{equation}
\end{center}
where $e$ is the elementary
charge, $\epsilon=2x_\textrm{B}\frac{M}{Q}$ with $M$
the \red{target} mass, and $\phi$ is the
azimuthal angle between the scattering and production planes \cite{Tre04}.
The {square of the} scattering amplitude $|\tau|^2$ can be written as
\begin{center}
\begin{equation}
|\tau|^{2} = |\tau_{\textrm{BH}}|^{2} +
|\tau_{\textrm{DVCS}}|^{2} + \textrm{I},
\end{equation}
\end{center}
with contributions from the \textrm{BH} process ($\tau_{\textrm{\textrm{BH}}}$),
the DVCS process
($\tau_{\textrm{DVCS}}$) and their interference term (I). These
contributions can be written as
\begin{eqnarray}
 |\tau_{\textrm{BH}}|^{2} &=&
 \frac{K_{\textrm{BH}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)} \left(c_{0,\textrm{unp}}^{\textrm{BH}} + \sum_{n=1}^2
  c_{n,\textrm{unp}}^{\textrm{BH}}\cos(n\phi)\right), \label{e:tbh}\\
|\tau_{\textrm{DVCS}}|^{2} &=&
K_{\textrm{DVCS}}\left(c_{0,\textrm{unp}}^{\textrm{DVCS}} +
\sum_{n=1}^2
c_{n,\textrm{unp}}^{\textrm{DVCS}}\cos(n\phi) + \lambda
s_{1,\textrm{unp}}^{\textrm{DVCS}}\sin\phi\right)\,\textrm{and}
\label{e:tdvcs}\\
 \textrm{I} &=& \frac{- e_\ell
K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}\left(c_{0,\textrm{unp}}^{\textrm{
I}}+
\sum_{n=1}^3 c_{n,\textrm{unp}}^{\textrm{I}}\cos(n\phi) + \lambda \sum_{n=1}^2
s_{n,\textrm{unp}}^{\textrm{I}}\sin(n\phi)\right),\label{e:ti}
\end{eqnarray}
where $\mathcal{P}_1(\phi)$ and $\mathcal{P}_2(\phi)$ are the lepton propagators
of the BH process, $\lambda$ is the
helicity of the lepton beam and $e_\ell$ is the unit charge of
  the lepton.  The
quantities $K_{\textrm{BH}}=1/(x_\textrm{B}^2t(1+\epsilon^2)^2)$,
$K_{\textrm{DVCS}}=1/Q^2$
and $K_{\textrm{I}}=1/(x_{\textrm{B}}yt)$ are kinematic factors, where
$y$ is the fraction of the beam energy carried by the virtual photon in
the target rest frame. A full
explanation of the Fourier coefficients [$c_{n,\textrm{unp}}^V,s_{n,\textrm{unp}}^W$]
($V\in[\textrm{BH,DVCS},\textrm{I}]$ and $W\in[\textrm{DVCS},\textrm{I}]$) can be found in ref.~\cite{Bel02b}.

@@

The $s_{n,\textrm{unp}}^{W}$ and $c_{n,\textrm{unp}}^{\textrm{\red{W}}}$ Fourier
coefficients depend on ``$\mathcal{C}$-functions'' \cite{Bel02b}, each of which is a
combination of complex\red{-valued} Compton Form Factors (CFFs). A CFF is a
\red{flavour-sum of} convolution\red{s} of GPD\red{s} with hard scattering kernel\red{s}. Contributions to the cross section \red{are} relatively suppressed by \red{factors that} may be kinematic in nature or due to the twist-level of the GPD\red{s appearing in that contribution}. Leading twist is twist-2. Typically, the contribution of a twist-$n$ GPD, and hence the corresponding CFF, is
suppressed by $\mathcal{O}(1/Q^{n-2})$.

>>>>

The four-fold differential cross section for the \red{exclusive} leptoproduction of real photons
from an unpolarised target can be written as \cite{Bel02b}
\begin{center}
\begin{equation}
\frac{\textrm{d}^4\sigma}{\textrm{d}x_{\textrm{B}}\textrm{d}Q^{2}\textrm{d}
|t|\textrm{d}\phi} =
\frac{x_{\textrm{B}}e^{6}}{32(2\pi)^{4} Q^{4}\sqrt{1+\epsilon^{2}}}
|\tau|^{2},
\end{equation}
\end{center}
where $e$ is the elementary
charge, $\epsilon=2x_\textrm{B}\frac{M}{Q}$ with $M$
the \red{target} mass, and $\phi$ is the
azimuthal angle between the scattering and production planes \cite{Tre04}.
The {square of the} scattering amplitude $|\tau|^2$ can be written as
\begin{center}
\begin{equation}
|\tau|^{2} = |\tau_{\textrm{BH}}|^{2} +
|\tau_{\textrm{DVCS}}|^{2} + \textrm{I},
\end{equation}
\end{center}
with contributions from the \textrm{BH} process ($\tau_{\textrm{\textrm{BH}}}$),
the DVCS process
($\tau_{\textrm{DVCS}}$) and their interference term (I). These
contributions can be written as
\begin{eqnarray}
 |\tau_{\textrm{BH}}|^{2} &=&
 \frac{K_{\textrm{BH}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)} \left(c_{0,\textrm{unp}}^{\textrm{BH}} + \sum_{n=1}^2
  c_{\textrm{unp},n}^{\textrm{BH}}\cos(n\phi)\right), \label{e:tbh}\\
|\tau_{\textrm{DVCS}}|^{2} &=&
K_{\textrm{DVCS}}\left(c_{0,\textrm{unp}}^{\textrm{DVCS}} +
\sum_{n=1}^2
c_{\textrm{unp},n}^{\textrm{DVCS}}\cos(n\phi) + \lambda
s_{1,\textrm{unp}}^{\textrm{DVCS}}\sin\phi\right)\,\textrm{and}
\label{e:tdvcs}\\
 \textrm{I} &=& \frac{- e_\ell
K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}\left(c_{0,\textrm{unp}}^{\textrm{
I}}+
\sum_{n=1}^3 c_{\textrm{unp},n}^{\textrm{I}}\cos(n\phi) + \lambda \sum_{n=1}^2
s_{\textrm{unp},n}^{\textrm{I}}\sin(n\phi)\right),\label{e:ti}
\end{eqnarray}
where $\mathcal{P}_1(\phi)$ and $\mathcal{P}_2(\phi)$ are the lepton propagators
of the BH process, $\lambda$ is the
helicity of the lepton beam and $e_\ell$ is the unit charge of
  the lepton.  The
quantities $K_{\textrm{BH}}=1/(x_\textrm{B}^2t(1+\epsilon^2)^2)$,
$K_{\textrm{DVCS}}=1/Q^2$
and $K_{\textrm{I}}=1/(x_{\textrm{B}}yt)$ are kinematic factors, where
$y$ is the fraction of the beam energy carried by the virtual photon in
the target rest frame. A full
explanation of the Fourier coefficients [$c_{\textrm{unp},n}^V,s_{\textrm{unp},n}^W$]
($V\in[\textrm{BH,DVCS},\textrm{I}]$ and $W\in[\textrm{DVCS},\textrm{I}]$) can be found in ref.~\cite{Bel02b}.

@@

The $s_{\textrm{unp}\red{,n}}^{W}$ and $c_{\textrm{unp}\red{,n}}^{\textrm{\red{W}}}$ Fourier
coefficients depend on ``$\mathcal{C}$-functions'' \cite{Bel02b}, each of which is a
combination of complex\red{-valued} Compton Form Factors (CFFs). A CFF is a
\red{flavour-sum of} convolution\red{s} of GPD\red{s} with hard scattering kernel\red{s}. Contributions to the cross section \red{are} relatively suppressed by \red{factors that} may be kinematic in nature or due to the twist-level of the GPD\red{s appearing in that contribution}. Leading twist is twist-2. Typically, the contribution of a twist-$n$ GPD, and hence the corresponding CFF, is
suppressed by $\mathcal{O}(1/Q^{n-2})$.
